## Exercise I
## ──────────

# Upload the file EconomistData.csv from your elearning platform 
##   These data consist of /Human Development Index/ and /Corruption
##   Perception Index/ scores for several countries.
#Transparency International’s (TI) Corruption Perceptions Index1 (CPI) 
#is an aggregate indicator that
#ranks countries in terms of the degree to which corruption 
#is perceived to exist among public officials and politicians. 
#It is a composite index drawing on corruption-related data from a variety of reputable
#institutions.
##   Original sources for these data are
##     [http://www.transparency.org/content/download/64476/1031428]



```{r}
ED<-read.csv("EconomistData.csv")
head(ED)
```


```{r}
plot(ED$CPI, ED$HDI)
```


```{r}

plot(ED$CPI, ED$HDI,xlab = "CPI",ylab="HDI", main="MY Plot",xlim=c(0,20),ylim = c(0,1.5),col='blue',pch=20)
```


```{r}
plot(ED$CPI, ED$HDI,xlab = "CPI",ylab="HDI", main="MY Plot",xlim=c(0,20),ylim = c(0,1.5))

points(ED$CPI[ED$Region=='Americas'],ED$HDI[ED$Region=='Americas'],col='red',pch=20)
```


dat <- read.csv(...)
#View(dat)
#head(dat)
```{r}


#2. Color the points in the previous plot blue.

#3. Color the points in the previous plot according to Region.

#4. Make the points bigger by setting size to 2


#5.Map the size of the points to HDI.Rank


#6/7. Create boxplots of CPI by Region and Overlay points on top of the box plots

```







```{r}
dat <- read.csv("EconomistData.csv")

```

```{r}
library(ggplot2)
```

##   1. Create a scatter plot with CPI on the x axis and HDI on the y axis.

```{r}
ggplot(dat, aes(x = CPI, y = HDI)) +  geom_point()
```


##   2. Color the points blue.

```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(color = "blue")

```

##   3. Map the color of the the points to Region.

```{r}
ggplot(dat, aes(x = CPI, y = HDI)) +   geom_point(aes(color = Region))

```

##   4. Make the points bigger by setting size to 2

```{r}

ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(aes(color = Region), size = 2)
```

##5. Map the size of the points to HDI.Rank

```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(aes(color = Region, size =  HDI.Rank))
```
## Exercise II
## ───────────

##   1. Re-create a scatter plot with CPI on the x axis and HDI on the 
##      axis (as you did in the previous exercise).


```{r}
ggplot(dat, aes(x = CPI, y = HDI)) +  geom_point()
```

##   2. Overlay a smoothing line on top of the scatter plot using
##      geom_smooth.

```{r}
ggplot(dat, aes(x = CPI, y = HDI)) +  geom_point()+geom_smooth()
```


##   3. Overlay a smoothing line on top of the scatter plot using
##      geom_smooth, but use a linear model for the predictions. Hint: see
##      `?stat_smooth'.

```{r}
ggplot(dat, aes(x = CPI, y = HDI)) +  geom_point()+geom_smooth(method = "lm")
```


```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point()+geom_smooth() + stat_smooth(method = "lm")
```


##   4. Overlay a smoothling line on top of the scatter plot using
##      geom_line. Hint: change the statistical transformation.



```{r}
dat$pred.CP <- predict(lm(HDI ~ CPI, data = dat))

p1 <- ggplot(dat, aes(x = CPI, y = HDI))

p1 + geom_point() + geom_line(aes(y = pred.CP))
```


##   5. Overlay a smoothing line on top of the scatter plot using
##      the default /loess/ method, but make it less smooth. Hint: see
##      `?loess'.

span is used for smooth
```{r}
dat$pred.CP <- predict(loess(HDI ~ CPI, data = dat,span = 0.15))

p1 <- ggplot(dat, aes(x = CPI, y = HDI))

p1 + geom_point() + geom_line(aes(y = pred.CP))
```


#smoothing method (function) to use, eg. "lm", "glm", "gam", "loess", "rlm".
#For method = "auto" the smoothing method is chosen based on the size of the 
#largest group (across all panels). loess is used for than 1,000 observations; 
#otherwise gam is used with formula = y ~ s(x, bs = "cs"). Somewhat anecdotally, 
#loess gives a better appearance, but is O(n^2) in memory, 
#so does not work for larger datasets.

